---
title: "Prediction for Covid-19"
output:
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
runtime: shiny
---


```{r}
library(keras)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(lubridate)
library(tensorflow)
library(reticulate)
library(plotly)
set.seed(7)
```

Data visualization
=========================================================================================
Plot
-------------------


### Confirmed Cases
```{r}
library(data.table)
datatrain <- read.csv('https://raw.githubusercontent.com/SHAAAAN/ds4ph-bme/master/project/train.csv')
datatest <- read.csv('https://raw.githubusercontent.com/SHAAAAN/ds4ph-bme/master/project/test.csv')
train_us=subset(datatrain, Country_Region=="US") 
train_us<-data.table(train_us)
a1<-train_us[,sum(ConfirmedCases),Date]
a2<-train_us[,sum(Fatalities),Date]
```
```{r}
renderPlotly({
k=ggplot(data = a1, mapping = aes(x = Date, y = V1)) +
  geom_line() +
  geom_point() +
  theme_economist()+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  labs(x ="date", y = "numbers", title = "Confirmed cases of COVID-19 in US") 
ggplotly(k)
})
```


### Prediction Model
```{r}
renderPlotly({
g=ggplot(data = a2, mapping = aes(x = Date, y = V1)) +
  geom_line() +
  geom_point() +
  theme_economist()+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  labs(x ="date", y = "numbers", title = "Fatalities of COVID-19 in US") 
ggplotly(g)
})
```


US Situation via SEIR model
=========================================================================================
Sidebar {.sidebar}
------------------------------------------------
SEIR Model function:       
Overview:       
The SEIR models the flows of people between four states: susceptible (S), exposed (E), infected (I), and resistant (R). Each of those variables represents the number of people in those groups. The parameters alpha and beta partially control how fast people move from being susceptible to exposed (beta), from exposed to infected (sigma), and from infected to resistant (gamma). This model has two additional parameters; one is the background mortality (mu) which is unaffected by disease-state, while the other is vaccination (nu). The vaccination moves people from the susceptible to resistant directly, without becoming exposed or infected.
Reference:  http://www.public.asu.edu/~hnesse/classes/seir.html


Plot
-------------------


### Confirmed Cases
```{r}
prediction <- read.csv('https://raw.githubusercontent.com/SHAAAAN/ds4ph-bme/master/project/predict_us.csv')
prediction <- prediction[1:100,]
```
```{r}
max=max(a1$V1)
prediction['real_conf']=0
prediction['real_conf'][1:58,]=a1$V1[48:105]
prediction['real_conf'][59:100,]=0
```
```{r}
renderPlotly({
k=ggplot(data = prediction, mapping = aes(x = realDate, )) +
  geom_point(aes(y = ConfirmedCases,),shape=3,color="red") +
  geom_point(aes(y = real_conf),shape=1,size=0.4,color="blue")+
  geom_vline(xintercept = 59, linetype = 2) +
  theme_economist()+
  annotate(geom="text", x= 69 ,y= max+50000, label='real data ends here')+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  labs(x ="date", y = "numbers", title = "Cumulated Actural vs. Predicted Confirmed cases of COVID-19 in US") 
ggplotly(k)
})
```


### Fatalities
```{r}
max2=max(a2$V1)
prediction['real_death']=0
prediction['real_death'][1:58,]=a2$V1[48:105]
prediction['real_death'][59:100,]=0
```
```{r}
renderPlotly({
k=ggplot(data = prediction) +
  geom_point(aes(x = realDate,y = Fatalities),shape=3,color="red") +
  geom_point(aes(x = realDate,y = real_death),shape=1,size=0.4,color="blue")+
  geom_vline(xintercept = 59, linetype = 2) +
  theme_economist()+
  annotate(geom="text", x= 69 ,y= max2+4000, label='real data ends here')+
  theme(axis.text.x=element_text(angle=90,hjust=1))+
  labs(x ="date", y = "numbers", title = "Cumulated Actural vs. Predicted Fatalities of COVID-19 in US") 
ggplotly(k)
})
```

US Situation via LSTM
=========================================================================================
Sidebar {.sidebar}
------------------------------------------------

### Data Select
```{r}
selectInput("country", label = "Country:",
            choices = c('US'), selected = 'US')
selectInput("state", label = "State:",
            choices = c('Alabama', 'Alaska', 'Arizona', 'Arkansas', 'California', 'Colorado',
                        'Connecticut', 'Delaware', 'District of Columbia', 
                        'Florida', 'Georgia', 'Guam', 'Hawaii', 'Idaho', 'Illinois', 'Indiana',
                        'Iowa', 'Kansas', 'Kentucky', 'Louisiana', 'Maine', 'Maryland',
                        'Massachusetts', 'Michigan', 'Minnesota', 'Mississippi', 'Missouri',
                        'Montana', 'Nebraska', 'Nevada', 'New Hampshire', 'New Jersey',
                        'New Mexico', 'New York', 'North Carolina', 'North Dakota',
                        'Ohio', 'Oklahoma', 'Oregon', 'Pennsylvania', 'Puerto Rico',
                        'Rhode Island', 'South Carolina', 'South Dakota', 'Tennessee',
                        'Texas', 'Utah', 'Vermont', 'Virgin Islands', 'Virginia',
                        'Washington', 'West Virginia', 'Wisconsin', 'Wyoming',
                        ''), selected = 'New York')
selectInput("type", label = "Type:",
            choices = c('ConfirmedCases','Fatalities'), selected = 'ConfirmedCase')
```

### Model Parameter Adjustment
```{r}
selectInput("epochs", label = "Epochs:",
            choices = c(30:300), selected = 50)
selectInput("look_back_p", label = "Look_back:", 
            choices = c(1:15), selected = 5)
selectInput("lstm", label = "layer lstm units:", 
            choices = c(1:15), selected = 4)
```

Plot
-------------------

### Prediction Model Polt
```{r}
renderPlotly({
  
dataframe <- read.csv('https://raw.githubusercontent.com/JialinKang/hello-world/master/train.csv')

df_US_NY <- subset(dataframe, Country_Region == input$country & Province_State == input$state & ConfirmedCases>0)

df_US_NY$Date <- df_US_NY$Date %>% ymd()
  
if(input$type == 'ConfirmedCases'){
  type = 5
}
else{
  type = 6
}

max_value <- max(df_US_NY[,type])
min_value <- min(df_US_NY[,type])
spread <- max_value - min_value

dataset_y <- (df_US_NY$ConfirmedCases - min_value)/spread

set_pre = 1:(length(dataset_y)+40)
max_value_x <- max(set_pre)
min_value_x <- min(set_pre)
spread_x <- max_value_x - min_value_x
dataset_x <-(set_pre - min_value_x)/ spread_x

look_back <- as.integer(input$look_back_p)

create_dataset <- function(dataset_x, dataset_y,
                           look_back = 1)
{
    l <- length(dataset_x)
    dataX <- array(dim = c(l - look_back, look_back))

    for (i in 1:ncol(dataX))
    {
        dataX[, i] <- dataset_x[i:(l - look_back + i - 1)]
    }

    dataY <- array(
        data = dataset_y[(look_back + 1):l],
        dim = c(l - look_back, 1))

    return(
        list(
            dataX = dataX,
            dataY = dataY))
}

future_size_x <- length(dataset_x) - length(dataset_y)

train <- dataset_y[1:length(dataset_y)]
future <- dataset_x[(length(dataset_y)- look_back):(length(dataset_x)-look_back)]

train_x <- dataset_x[1:length(dataset_y)]
future_x <- dataset_x[(length(dataset_y)-look_back):(length(dataset_x)-look_back)]



trainXY <- create_dataset(train_x, train, look_back)
futureXY <- create_dataset(future_x, future, look_back)

dim_train <- dim(trainXY$dataX)
dim_future <- dim(futureXY$dataX)

# reshape input to be [samples, time steps, features]
dim(trainXY$dataX) <- c(dim_train[1], 1, dim_train[2])
dim(futureXY$dataX) <- c(dim_future[1], 1, dim_future[2])

model <- keras_model_sequential()

model %>%
    layer_lstm(
        units = input$lstm,
        input_shape = c(1, look_back)) %>%
    layer_dense(
        units = 1) %>%
    compile(
        loss = 'mean_squared_error',
        optimizer = 'adam') %>%
    fit(trainXY$dataX,
        trainXY$dataY,
        epochs = input$epochs,
        batch_size = 1,
        verbose = 2)

trainScore <- model %>%
    evaluate(
        trainXY$dataX,
        trainXY$dataY,
        verbose = 2)


futureScore <- model %>%
    evaluate(
        futureXY$dataX,
        futureXY$dataY,
        verbose = 2)

sprintf(
    'Train Score: %.4f MSE (%.4f RMSE)',
    trainScore * spread^2,
    sqrt(trainScore) * spread)


sprintf(
    'Future Score: %.4f MSE (%.4f RMSE)',
    futureScore * spread^2,
    sqrt(futureScore) * spread)

trainPredict <- model %>%
    predict(
        trainXY$dataX,
        verbose = 2)

futurePredict <- model %>%
    predict(
        futureXY$dataX,
        verbose = 2
    )

trainPredict <- trainPredict * spread + min_value
futurePredict <- futurePredict * spread + min_value

df <- data.frame(
    index = 1:length(dataset_y),
    value = dataset_y * spread + min_value,
    type = 'raw') %>%
    rbind(
        data.frame(
            index = 1:length(trainPredict) + look_back,
            value = trainPredict,
            type = 'train')) %>%
    rbind(
        data.frame(
            index = 1:length(futurePredict) + length(dataset_y),
            value = futurePredict,
            type = 'future'))

p <- ggplot(data = df) +
    geom_line(
        mapping = aes(
            x = index,
            y = value,
            color = type)) +
    geom_point(
        mapping = aes(
            x = index,
            y = value,
            color = type)) +
    geom_vline(
        xintercept = length(train) + 0.5 -60, linetype = 2) +
    geom_vline(
        xintercept = length(train) + 0.5 -45, linetype = 2) +
    geom_vline(
        xintercept = length(train) + 0.5 -30, linetype = 2) +
    geom_vline(
        xintercept = length(train) + 0.5 -15, linetype = 2) +
    geom_vline(
        xintercept = length(train) + 0.5    , linetype = 2) +
    geom_vline(
        xintercept = length(train) + 0.5 +15, linetype = 2) +
    geom_vline(
        xintercept = length(train) + 0.5 +30, linetype = 2) +
    theme_economist() +
    scale_color_economist()+
    annotate(geom="text", x= length(train) +0.5 -60 ,y= 1, label='03-02')+
    annotate(geom="text", x= length(train) +0.5 -45, y= 1, label='03-17')+
    annotate(geom="text", x= length(train) +0.5 -30, y= 1, label='04-01')+
    annotate(geom="text", x= length(train) +0.5 -15, y= 1, label='04-16')+
    annotate(geom="text", x= length(train) +0.5    , y= 1, label='05-06')+
    annotate(geom="text", x= length(train) +0.5 +15, y= 1, label='05-21')+
    annotate(geom="text", x= length(train) +0.5 +30, y= 1, label='06-15')+
    labs(x ="Date", y = input$type, title = "Prediction Model of COVID-19 in US") 

ggplotly(p)
})
```

### Model structure

```{r}
renderPrint({
  model <- keras_model_sequential()

  look_back <- as.integer(input$look_back_p)

model %>%
    layer_lstm(
        units = input$lstm,
        input_shape = c(1, look_back)) %>%
    layer_dense(
        units = 1) %>%
    compile(
        loss = 'mean_squared_error',
        optimizer = 'adam')
print(summary(model))
})
```